---
title: "Timeline"
author: "granpiero"
date: "2026-02-03"
description: "planning network"
categories: [news]
editor: 
  markdown: 
    wrap: sentence
---

> GANTT chart

```{mermaid}
gantt
    title Parallel Tasks Example
    dateFormat  YYYY
    axisFormat  %Y

    section Flow
    FR_start    :fr_st, 2606, 1y
    1_AT_search_address  :at_search, after fr_st, 9y
    AT_tour  :at_tour, after fr_st, 9y
    MISC_checks  :at_checks, after fr_st, 9y
    2_AT_new_address  :at_addr, after at_search, 11y
    ENSAP_move   :ensap, after at_search, 11y
    SIRP_move    :sirp_move, after at_search, 11y
    MISC_move   :misc_move, after at_search, 11y
    3_AT_install   :at_install, after at_addr, 8y
    AT_Meldungen   :misc_move, after at_addr, 4y
    DGFIP        :dgfip, after sirp_move, 4y
    APR-Pâques   :apr, 2615, 4y
    JUL      :jul, 2627, 4y


```

1. **1_AT_search_address** includes all preminary actions: at_bank (that can be preempted) and at_Steuerberater.
2. de **2_AT_new_address** découle de l'obtention d'un domicile et active ENSAP_move,  SIRP_move, DGFIP
- SIRP_move take input of **new address** / **new_bank** for **new_salary** with a delay of 2 months
- ENSAP_move takes input of **new_address** for transfer of ENSAP Pension from Limoges to Nantes and confirms french RIB. 
- DGFIP just needs to be notified of **new_address**. Tax return is performed on line as usual with two declarations around ut-off date.s
3. **3_AT_install** includes AT_Meldezettel and physical Erstanmeldung Steuer.

4. **MISC_move** includes all FR contract changes (mainly of address eg for banks and providers and taxe foncière)

5. cf **AT_Anmeldungen** for 3 details

6. **MISC_checks** includes telecom for SIM.fr Data in AT and SIM.tph to AT. 

```{r BOM, echo=FALSE}
bom <- tibble::tribble(
   ~node, ~category, ~params,
   "contrat_location","2_AT_new_address",NA ,
   "ENSAP_move","2_AT_new_address",NA ,
   "SIRP_move","2_AT_new_address",NA ,
   "AT_Meldezettel","3_AT_install",NA ,
   "AT_Erstanmeldung_Tax","3_AT_install",NA ,
   "MISC_move","2_AT_new_address",NA ,
   "DGFIP","3_AT_install",NA ,
   "AT_install","3_AT_install",NA ,
   "porte blindée","1_AT_search_address",NA ,
   "tax_future_review","1_AT_search_address",NA ,
   "steuerberater","1_AT_search_address",NA ,
   "steueramt","1_AT_search_address",NA ,
   "chrétiens","1_AT_search_address",NA ,
   "immo search","1_AT_search_address",NA ,
   "bank digital","1_AT_search_address",NA ,
   "explo tour","1_AT_search_address",NA ,
   "test_telecom","1_AT_search_address",NA ,
   "CGR_contact","1_AT_search_address",NA ,
   "CSG_avie_remb","any",NA ,

) 

bom.arrange <- bom |> 
  dplyr::select(dplyr::matches("^node|^category")) |>
  dplyr::relocate(category) |>
  dplyr::arrange(category) 

bom.json <- bom.arrange |>
  jsonlite::toJSON()

## bom.json |>  jsonlite::prettify()

bom.arrange |>
  gt::gt()
```

```{r TRIBL, echo=FALSE, eval=FALSE}
tibble::tribble(
  ~action,~objectif,
  "Tax_Future","simulations delta",
  "SIRP","formulaire & délai",
  "ENSAP","formulaire & délai",
  "DGFIP","formulaire & délai",
  "Anmeldung","formulaire & délai 3 jours !",
  "AT_Bank","",
  "AT_Domicile","",
  "Cutoff","optimum f(cutoff)",
  "Budget","lister dépenses",
) |>
  gt::gt()
```

