---
title: "Full Coverage"
author: "granpiero"
date: "2026-05-14"
description: "How to scan whole market"
categories: [search]
editor: 
  markdown: 
    wrap: sentence
execute:
  echo: false
---

> HowTo

The whole‑market method to track all new listings in Villach/Klagenfurt is to combine three layers:  
1) **Portal‑level** search agents (covering 90% of the market)  
2) **Agency‑level** feeds (covering the remaining 10%)  
3) A weekly **manual sweep** (to catch anything the algorithms miss)

```{r}
source(here::here("src/_common.R"))
db_() |>
  dplyr::select(-dplyr::matches("^col")) |>
  dplyr::filter(type %in% "portal90") |>
  gt::gt() |>
  gt::tab_header("How to cover the market")
```

```{r}
db_() |>
  dplyr::select(-dplyr::matches("^col")) |>
  dplyr::filter(type %in% "agent") |>
  gt::gt() |>
  gt::tab_header("How to cover the market")
```



This gives you complete coverage of the market — not just Willhaben/ImmoScout, but also REMAX, Perkonig, Schick, NPK, etc.  
Below is the full system, structured and actionable.

---

1) Set up portal‑level search agents (covers ~90% of the market)

These are the only tools that reliably capture almost all new listings.  
Each bullet begins with a Guided Link so you can expand any part.

- Willhaben Suchagent — The single most important source; private sellers + agencies.  
  Create 2 agents:  
  - Miet_T2 in Mietwohnungen, bis 65m² , 2-3 Zimmer, Balkon, Fahrstuhl, Parkplatz, Klagenfurt, Villach, Klagenfurt Land, Villach Land
  - Kauf_T2 in Eigentumswohnung, bis € 280.000, 50-65m² , 2-3 Zimmer, Balkon, Fahrstuhl, Parkplatz, Klagenfurt, Villach, Klagenfurt Land, Villach Land


- ImmoScout24 Suchagent — Best for agency listings and new builds.  
  Use filters:  
  - Region: Villach + Klagenfurt  
  - Price: €150–300k  
  - Rooms: 2  
  - Features: Lift, Parkplatz

- Immowelt Suchagent — Captures agencies that don’t list on Willhaben.

- Der Standard Immobilien Suchagent — Good for private sellers and older buildings.

These four agents alone give you 90%+ coverage of all new listings.

---

2) Add agency‑level feeds (captures the missing 10%)

Some agencies delay posting to portals or post only on their own site for 24–72 hours.  
These are the agencies that matter in Villach/Klagenfurt:

- REMAX Villach/Klagenfurt — Large inventory, often first to publish.  
- Perkonig Klagenfurt — Strong in Klagenfurt mid‑range flats.  
- Schick Immobilien Villach — Very active in Völkendorf/Lind.  
- NPK Immobilien — Dominant in Villach.  
- Belvimo Klagenfurt — Good for renovated 2000s buildings.  
- Immobilien Consulting Villach — Often has early postings.

You don’t need to check them daily — twice per week is enough.

These agencies frequently handle Lind properties and often list them before portals:
- ERA Immobilien Villach
- VBV Villach
- Kohl Immobilien
- Immobilien Dr. Schwanzer
- Realitäten Perntner

---

3) Perform a weekly sweep (catches everything the agents miss)

This is the “insurance layer” that ensures you never miss a listing.

- Search Willhaben manually  
  Sort by “Neueste zuerst” and scan the last 48 hours.

- Search ImmoScout manually  
  Sort by “Neu eingestellt”.

- Check Facebook groups  
  Private sellers often post here before portals:  
  - “Immobilien Villach Privat”  
  - “Immobilien Klagenfurt Privat”

- Check developer pages  
  For rare new builds in Villach/Klagenfurt.

This sweep takes 10–12 minutes per week and guarantees full coverage.

---

4) Optional: Build a “priority watchlist” of buildings

Since you already have a shortlist of the best buildings, you can track them directly:

- Track supply in target buildings  
  Search each building name weekly on Willhaben + ImmoScout.

This is how you catch rare units in Lind, Völkendorf, Warmbad, Landskron, Viktring, etc.

---

5) The complete system (summary)

| Step | Tool | Coverage | Frequency |
|------|------|----------|-----------|
| Portal search agents | Willhaben, ImmoScout, Immowelt, Der Standard | ~90% | Automatic |
| Agency feeds | REMAX, Perkonig, Schick, NPK, Belvimo | +10% | 2×/week |
| Weekly sweep | Manual checks + FB groups | 100% | Weekly |
| Building watchlist | Your top 10–12 buildings | Rare gems | Weekly |

This is the complete, whole‑market tracking system used by professional buyers’ agents.

---

Want me to automate this into a weekly checklist you can follow in 5 minutes?
I can generate a 5‑minute weekly routine tailored to Villach/Klagenfurt.